Perceptions and Preferences for Meritocracy

### 2020-04-23 docs/index.Rmd
Update paper
Render completo luego de pull-requests

last website update: `r format(Sys.time(), "%A %d %B %Y %X")`

@@

- The other three tabs follow the logic of the [IPO protocol](https://github.com/juancarloscastillo/ipo) for academic workflows, based on three main components = **I**nput -> **P**roduction -> **O**utput. Here we show only one the main parts of each component: Data -> Analysis -> Paper. The complete reproducible files are in the [Github repo: https://juancarloscastillo.github.io/merit-scale/](https://juancarloscastillo.github.io/merit-scale/)

>>>>

Last update: `r format(Sys.time(), "%A %d %B %Y %X")`

@@

- The tabs follow the logic of the [IPO protocol](https://github.com/juancarloscastillo/ipo) for academic workflows, based on three main components = **I**nput -> **P**roduction -> **O**utput. Here we show only one the main parts of each component: Data -> Analysis -> Paper. The complete reproducible files are in the [Github repo: https://juancarloscastillo.github.io/merit-scale/](https://juancarloscastillo.github.io/merit-scale/)

### 2020-04-23 docs/paper.Rmd
Render completo luego de pull-requests

---
title: "Perceptions and Preferences for Meritocracy"
css: "../input/bib/style.css"
linestretch: '1.5'
link-citations: yes
output:
    html_document:
        number_sections: true
        toc: true
        toc_float: true
        smart: false
linkcolor: blue
bibliography:
  - ../input/bib/EconomiaMoral.bib
  - ../input/bib/meritocracy.bib
editor_options: 
  chunk_output_type: console
---

@@

b. Beliefs: the "get ahead" battery refers to "how important you think it is", considered by Mijs as a belief in meritocracy. Nevertheless, another version of this same battery asks about "how important you think it _should_ be". Which one of both is the "belief"? If we consider belief as related to a normative content, actually the more close version is the "should be", being the other one more close to the perception of the situation. Such distinction was already made by @duru-bellat_whos_2012, who used the item "how important should the number of years spent in education and training be in deciding how much money people ought to earn?" for "desired" meritocracy, whereas for "perceived" meritocracy they use two items: “Would you say that in your country, people are rewarded for their efforts?” and “... people are rewarded for their skills?”. Is the belief in meritocracy a perception or a preference? A comprehensive measurement should be in line with what @duru-bellat_whos_2012 did, in order to open up possibilities of analyzing whether perceptions and preferences are actually the same (i.e. correlation close to 1) or they are different aspects of the same phenomenon. As @son_hing_merit_2011-1 have pointed out, "People can believe that outcomes ought to be distributed on the basis of merit and yet vary in their perceptions of whether this is how society currently operates" (p. 435). Accordingly, we suggest that the use of the term belief is confusing, being more accurate to speak about meritocratic perceptions and preferences.

@@

## Data
The Netquest company ([website](www.netquest.cl)) applied the online survey during December and January. The online survey distributed by the company was scheduled on the platform Qualtrics ([website](www.Qualtrics.com)). The sample was selected from a non-probabilistic design in three large cities in Chile. The quota method based on age, sex and educational level was used. Quotas were generated based on the survey of the Public Studies Center (CEP, 2019), which has a high prestige in the country. A total sample of 2141 people was collected, excluding those who did not answer the questions on the scale and those who did not accept informed consent. The representativeness of the sample is not satisfactory because, although the proportion by age and sex is consistent with the estimates of the CEP survey, a bias towards high educational levels is evident (as detailed in Annex __X__). This limitation must be considered when making inferences about the population.

@@

>Diagrama de flujo de la encuesta, orden de la escala.

@@

The proposed scale of perceptions and preferences about meritocracy consists of 8 indicators that are grouped into the 4 dimensions indicated. The questions are adaptations of the "get ahead" scale. the terms of of this scale were used (i.e talent, effort, contacts and wealthy parents) which are included in different investigations on meritocracy [@mijs_paradox_2019; @duru-bellat_whos_2012; @reynolds_perceptions_2014]. Unlike this scale, this proposal adds the difference between perceptions and preferences. In addition, a comparative component is incorporated into the question that refers to differences between people with little or fed up with some attribute (e.g. effort, contacts).The eight items ordered according to dimensions are presented in Table 2. These 8 likert-type items have 5 response alternatives ranging from "I completely agree" (5) to "I completely disagree"(1). According to the recommendations of Xia and Yang ([2018](https://link.springer.com/article/10.3758/s13428-018-1055-2)) for categorical data, we present below a table with the descriptive table and another with correlations between the items on the scale.
=======
The field work was conducted during November and December of 2019 in Chile, obtaining a final sample of 2200 individuals, but considering that we use cases with complete information, the final analytical sample has 2141 observations.

@@

```{r echo=FALSE,results='asis', warning=FALSE, message=FALSE}
load(file = "../input/data/proc/dat04.RData")
library(stargazer)
stargazer(dat04,type = "html",
          title = "Descriptive statistics",
          font.size = "small",
          median = TRUE,
          header=FALSE,
          digit.separator = "",
          digits = 2,
          covariate.labels = c("A. pc.effort", "B. pc.talent","C. pc.wpart","D. pc.netw","E. pf.effort","F. pf.talent","G. pf.wpart", "H. pf.netw"))
```

@@

>>>>

---
title: "Perceptions and Preferences for Meritocracy"
css: "../input/css/custom.css"
linestretch: '1.5'
link-citations: yes
output:
    html_document:
        number_sections: true
        toc: true
        toc_float: true
        smart: false
linkcolor: blue
bibliography:
  - ../input/bib/EconomiaMoral.bib
  - ../input/bib/meritocracy.bib
editor_options:
  chunk_output_type: console
---

@@

b. Beliefs: the "get ahead" battery refers to "how important you think it is", considered by Mijs as a belief in meritocracy. Nevertheless, another version of this same battery asks about "how important you think it _should_ be". Which one of both is the "belief"? If we consider belief as related to a normative content, actually the more close version is the "should be", being the other one more close to the perception of the situation. Such distinction was already made by @duru-bellat_whos_2012, who used the item "how important should the number of years spent in education and training be in deciding how much money people ought to earn?" for "desired" meritocracy, whereas for "perceived" meritocracy they use two items: “Would you say that in your country, people are rewarded for their efforts?” and “... people are rewarded for their skills?”. Is the belief in meritocracy a perception or a preference? A comprehensive measurement should be in line with what @duru-bellat_whos_2012 did, in order to open up possibilities of analyzing whether perceptions and preferences are actually the same (i.e. correlation close to 1) or they are different aspects of the same phenomenon. As @son_hing_merit_2011-1 have pointed out, "People can believe that outcomes ought to be distributed on the basis of merit and yet vary in their perceptions of whether this is how society currently operates" (p. 435). Accordingly, we suggest that the use of the term belief is confusing, being more accurate to speak about meritocratic perceptions and preferences.
Uso conjunto de percepción y preferencias.

@@

## Data

The Netquest company ([website](www.netquest.cl)) applied the online survey during December and January. The online survey distributed by the company was scheduled on the platform Qualtrics ([website](www.Qualtrics.com)). The sample was selected from a non-probabilistic design in three large cities in Chile. The quota method based on age, sex and educational level was used. Quotas were generated based on the survey of the Public Studies Center (CEP, 2019), which has a high prestige in the country. A total sample of 2141 people was collected, excluding those who did not answer the questions on the scale and those who did not accept informed consent. The representativeness of the sample is not satisfactory because, although the proportion by age and sex is consistent with the estimates of the CEP survey, a bias towards high educational levels is evident (as detailed in Annex __X__). This limitation must be considered when making inferences about the population.

@@

!!! Diagrama de flujo de la encuesta, orden de la escala.

@@

The proposed scale of perceptions and preferences about meritocracy consists of 8 indicators that are grouped into the 4 dimensions indicated. The questions are adaptations of the "get ahead" scale. the terms of of this scale were used (i.e talent, effort, contacts and wealthy parents) which are included in different investigations on meritocracy [@mijs_paradox_2019; @duru-bellat_whos_2012; @reynolds_perceptions_2014]. Unlike this scale, this proposal adds the difference between perceptions and preferences. In addition, a comparative component is incorporated into the question that refers to differences between people with little or fed up with some attribute (e.g. effort, contacts).The eight items ordered according to dimensions are presented in Table 2. These 8 likert-type items have 5 response alternatives ranging from "I completely agree" (5) to "I completely disagree"(1). According to the recommendations of Xia and Yang ([2018](https://link.springer.com/article/10.3758/s13428-018-1055-2)) for categorical data, we present below a table with the descriptive table and another with correlations between the items on the scale.

The field work was conducted during November and December of 2019 in Chile, obtaining a final sample of 2200 individuals, but considering that we use cases with complete information, the final analytical sample has 2141 observations.

@@

```{r echo=FALSE,results='asis', warning=FALSE, message=FALSE}
load(file = "input/data/proc/dat04.RData")
library(stargazer)
stargazer(dat04,type = "html",
          title = "Descriptive statistics",
          font.size = "small",
          median = TRUE,
          header=FALSE,
          digit.separator = "",
          digits = 2,
          covariate.labels = c("A. pc.effort", "B. pc.talent","C. pc.wpart","D. pc.netw","E. pf.effort","F. pf.talent","G. pf.wpart", "H. pf.netw"))
```

@@

# Conclusiones

uso conjunto percepciones-preferencias
